---
title: "Activity: Nuclear Reactors"
author: "Jared Hayes"
output: html_notebook
---

```{r}
library(tidyverse)
library(rvest)
```

## Scrape the Data 

```{r}
#My code here.... 
page <- "https://en.wikipedia.org/wiki/List_of_commercial_nuclear_reactors"
tableList <- page %>%
  read_html() %>%
  html_nodes(css = "table") %>%
  html_table(fill = TRUE)

Japan<-tableList[[21]]
```


## Your turn: In what ways is the table tidy? How is it not tidy? What’s different about it from a tidy table?

It is tidy because each row is a case. It is not tidy because each value does not have its own cell. Values share cells because the cells contain a list of information. It is also not tidy because each variable does not have its own column variables share one column. 


## Your Turn: Plot Net Generation Capacity vs Construction Date

```{r}
library(lubridate)
#my code here 
Japan<-tableList[[21]]
Japan<-Japan[-1,1:9]
Japan <-
  Japan %>%
  rename(name = Plantname, 
         reactor = `UnitNo.`,
         model = Model,
         status = Status, 
         netMW = `Capacity(MW)`,
         construction = `Beginbuilding`,
         operation = `Commercialoperation`, 
         closure = Closed)%>%
mutate(construction =dmy(construction),
         operation = dmy(operation),
         closure = dmy(closure),
         netMW = as.numeric(netMW),
         country = "Japan")

ggplot(Japan,aes(x=construction,y=netMW,color=Type))+
  geom_point()
```


## Your Turn: Scrape & Clean China Data (then merge with Japan)

```{r}
#my code here... 
China<-tableList[[10]]
China<-China[-1,1:9]
China <-
  China %>%
  filter(row_number() > 1) %>%
  rename(name = Plantname, 
         reactor = `UnitNo.`,
         model = Model,
         status = Status, 
         netMW = `Capacity(MW)`,
         construction = `Beginbuilding`,
         operation = `Commercialoperation`, 
         closure = Closed)%>%
mutate(construction =dmy(construction),
         operation = dmy(operation),
         closure = dmy(closure),
         netMW = as.numeric(netMW),
         country = "China")
combined_data<-bind_rows(Japan,China)
```



## Your Turn: Reconstruct Info Graphic of Japan Reactors (or other country of interest)

```{r}
#My code here
Japan <- Japan %>%
  mutate(interval = operation - construction)

# Plot time interval for Japan
ggplot(Japan, aes(x = construction, xend = operation, y = name, yend = name)) +
  geom_segment(aes(color = Type)) +
  geom_point(aes(x=closure,y=name,shape=status))+
  labs(title = "Time Interval from Start of Construction to Operation",
       x = "Date",
       y = "Reactor Name",
       color = "Reactor Type",
       group="Status")

```